---
title: "Computational Reproducibility"
author: "Fred LaPolla"
date: "10/14/2020"
output: html_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown file

This file, an R Markdown lets you combine plain text, in the white spaces, and code chunks, in the gray. The text is not really code, but can be used to communicate, while the code chunks let you combine the actual analysis you are running alongside the results. This means someone can see exactly what you did to get your results.

To add a chunk either click on the green Insert button and choose R or hit Command + Option + i (Mac) or Ctrl + Alt + i (PC)

```{r}
3+3
```

## Homework

1) Create an R Project to pull this file from GitHub. 

2) Please describe one of the ways that Wilson et. al. suggest is a good practice for computational reproducibility and how a tool like R can be used. Write your answer below.

One good practice is to save your raw data and document steps and comments in the programs/script. To use R or other commonly used data analysis tools, you just need to load the raw data, which is unchanged among different analysis. Then in the code you can add comment to clarify what step you did and what values you expected to get from it. The plots/figures can generated automatically when you run the data. This good practice makes the data analysis more clear and reproducible to both the collaborators and yourself.

3) Add a code chunk and find the square root of 4 to the 13th power. If you are unsure of what command to use, google it. 

```{r}
sqrt(4^13)
```

4) Push this homework to the GitHub repository for the homework. 





